Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-09 paper/experiments.tex
Paper update

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
         Function           & Dimension        & Search domain             \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
         Alpine1            & 5                & $[-10, 10]^5$             \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Eggholder          & 2                & $[-512, 512]^2$           \\
         Ackley2            & 2                & $[-32, 32]^2$             \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table*}[t]
    \centering
    \caption{Optimization results of the benchmark functions}
    \label{tab:result_analytical}
    \begin{tabular}{lllllllllll}
        \toprule
                & Eggholder                &  Branin              &  Alpine1              & Hartmann6                   \\ \midrule
        MACE-1  & 87.65$\pm$75.83          &  1.05e-5$\pm$1.31e-5          & 2.66305$\pm$1.05844            & 0.0646869$\pm$0.0621189 \\
        LCB-1   & 153.9$\pm$112.8          &  6.86e-5$\pm$1.13e-4          & 5.66812$\pm$1.76973            & 0.125565$\pm$0.122684   \\
        EI-1    & 172.8$\pm$132.2          &  1.62e-2$\pm$1.63e-2          & 2.46061$\pm$1.56079            & 0.110561$\pm$0.146809   \\
        MACE-4  & 46.38$\pm$40.89          &  \textbf{4.62e-6$\pm$6.64e-6} & \textbf{0.903805$\pm$0.835209} & \textbf{0.0275738$\pm$0.052254}  \\
        BLCB-4  & 56.86$\pm$35.91          &  4.32e-5$\pm$6.33e-5          & 1.8843$\pm$0.938873            & 0.06447$\pm$0.0621176   \\
        EI-LP-4 & \textbf{44.68$\pm$56.45} &  2.11e-2$\pm$1.84e-2          & 1.0059$\pm$0.456865            & 0.0540446$\pm$0.0558557 \\
        qKG-4   & 106.4$\pm$67.64          &  2.65e-1$\pm$2.70e-1          & 3.01513$\pm$1.13414            & 0.47134$\pm$0.18939     \\
        qEI-4   & 72.13$\pm$52.08          &  3.29e-4$\pm$1.14e-3          & 2.7074$\pm$1.05145             & 0.186088$\pm$0.116323   \\
        \hline
                & Ackley2                       &  Rosenbrock2               & Ackley10              & Rosenbrock10        \\ \midrule
        MACE-1  & 1.71474$\pm$1.12154           &  0.026173$\pm$0.051189              & 3.1348$\pm$0.447874           & 499.697$\pm$300.899 \\
        LCB-1   & 1.624$\pm$0.926437            &  0.0201124$\pm$0.0205367            & 3.14797$\pm$0.519164          & 517.944$\pm$288.955 \\
        EI-1    & 1.0136$\pm$0.985858           &  13.5508$\pm$9.52734                & 18.8006$\pm$0.652136          & 1367.08$\pm$637.507 \\
        MACE-4  & 1.07906$\pm$0.886466          &  \textbf{0.00095416$\pm$0.00093729} & \textbf{2.56439$\pm$0.535488} & \textbf{158.116$\pm$50.0024} \\
        BLCB-4  & 1.40051$\pm$1.02849           &  0.00191986$\pm$0.00180895          & 3.27543$\pm$0.735501          & 406.819$\pm$127.351 \\
        EI-LP-4 & \textbf{0.284265$\pm$0.24634} &  2.73645$\pm$2.05923                & 18.2682$\pm$0.608564          & 721.351$\pm$327.365 \\
        qKG-4   & 5.59394$\pm$1.80595           &  5.03976$\pm$3.72014                & 18.197$\pm$0.764103           & 705.112$\pm$412.762 \\
        qEI-4   & 2.87373$\pm$1.02405           &  10.1881$\pm$15.0432                & 18.3686$\pm$0.501869          & 655.208$\pm$340.954 \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

@@

We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
acquisition functions, the sequential EI and LCB based Bayesian optimization
are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
respectively.

The mean convergence plots of the tested algorithms on the benchmark functions are
given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and
Table~\ref{tab:result_analytical}, when running in sequential mode (MACE-1 in Table~\ref{tab:result_analytical} and Figure~\ref{fig:CovPlotBenchmark}), the MACE
algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE.

@@

\begin{table}[h]
    \centering
    \caption{Optimization results of the operational amplifier}
    \label{tab:result_opamp}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & -678.174$\pm$21.7445 \\
        LCB-1     & -607.583$\pm$51.9786 \\
        EI-1      & -532.555$\pm$66.942  \\
        MACE-4    & \textbf{-690.3$\pm$0.104963}  \\
        BLCB-4    & -665.442$\pm$23.066  \\
        EI-LP-4   & -636.675$\pm$35.7359 \\
        \bottomrule
    \end{tabular}
\end{table}

The mean convergence plot for the sequential and batch runs are given in
Figure~\ref{fig:resDAC2014}, the mean and standard deviation of the final
optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
seen, on average, the batch MACE algorithm had the fastest convergence rate
compared with the sequential MACE algorithm and other parallel algorithms. It
should also be noted that the final optimized FOM values given by MACE-4 have
very small deviation (0.105) compared with other algorithms.

@@

@@

\begin{table}[]
    \centering
    \caption{Optimization results of the power amplifier}
    \label{tab:result_PA}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results               \\ \midrule
        MACE-1    & -4.08608$\pm$0.296647 \\
        LCB-1     & -3.78533$\pm$0.335532 \\
        EI-1      & -3.36407$\pm$0.307489 \\
        MACE-4    & \textbf{-4.31762$\pm$0.347026} \\
        BLCB-4    & -4.20266$\pm$0.211102 \\
        EI-LP-4   & -4.07233$\pm$0.244436 \\
        \bottomrule
    \end{tabular}
    \vskip -0.2in
\end{table}

\begin{figure}[]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
\end{figure}

@@

For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the Figure of Merit $FOM$ is constructed as
$$
\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
$$

@@

\begin{figure}[]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
        \caption{Optimization results of the class-E power amplifier}
        \label{fig:resClassE}
    \end{center}
    \vskip -0.2in
\end{figure}

>>>>

@@

\begin{table}[!htb]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
         Function           & Dimension        & Search domain             \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
         Alpine1            & 5                & $[-10, 10]^5$             \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Eggholder          & 2                & $[-512, 512]^2$           \\
         Ackley2            & 2                & $[-32, 32]^2$             \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table*}[!htb]
    \centering
    \caption{Optimization results of the benchmark functions}
    \label{tab:result_analytical}
    \begin{tabular}{lllllllllll}
        \toprule
                & Eggholder                &  Branin              &  Alpine1              & Hartmann6                   \\ \midrule
        MACE-1  & 87.65$\pm$75.83          &  1.05e-5$\pm$1.31e-5          & 2.66305$\pm$1.05844            & 0.0646869$\pm$0.0621189 \\
        LCB-1   & 153.9$\pm$112.8          &  6.86e-5$\pm$1.13e-4          & 5.66812$\pm$1.76973            & 0.125565$\pm$0.122684   \\
        EI-1    & 172.8$\pm$132.2          &  1.62e-2$\pm$1.63e-2          & 2.46061$\pm$1.56079            & 0.110561$\pm$0.146809   \\
        MACE-4  & 46.38$\pm$40.89          &  \textbf{4.62e-6$\pm$6.64e-6} & \textbf{0.903805$\pm$0.835209} & \textbf{0.0275738$\pm$0.052254}  \\
        BLCB-4  & 56.86$\pm$35.91          &  4.32e-5$\pm$6.33e-5          & 1.8843$\pm$0.938873            & 0.06447$\pm$0.0621176   \\
        EI-LP-4 & \textbf{44.68$\pm$56.45} &  2.11e-2$\pm$1.84e-2          & 1.0059$\pm$0.456865            & 0.0540446$\pm$0.0558557 \\
        qKG-4   & 106.4$\pm$67.64          &  2.65e-1$\pm$2.70e-1          & 3.01513$\pm$1.13414            & 0.47134$\pm$0.18939     \\
        qEI-4   & 72.13$\pm$52.08          &  3.29e-4$\pm$1.14e-3          & 2.7074$\pm$1.05145             & 0.186088$\pm$0.116323   \\
        \hline
                & Ackley2                       &  Rosenbrock2               & Ackley10              & Rosenbrock10        \\ \midrule
        MACE-1  & 1.71474$\pm$1.12154           &  0.026173$\pm$0.051189              & 3.1348$\pm$0.447874           & 499.697$\pm$300.899 \\
        LCB-1   & 1.624$\pm$0.926437            &  0.0201124$\pm$0.0205367            & 3.14797$\pm$0.519164          & 517.944$\pm$288.955 \\
        EI-1    & 1.0136$\pm$0.985858           &  13.5508$\pm$9.52734                & 18.8006$\pm$0.652136          & 1367.08$\pm$637.507 \\
        MACE-4  & 1.07906$\pm$0.886466          &  \textbf{0.00095416$\pm$0.00093729} & \textbf{2.56439$\pm$0.535488} & \textbf{158.116$\pm$50.0024} \\
        BLCB-4  & 1.40051$\pm$1.02849           &  0.00191986$\pm$0.00180895          & 3.27543$\pm$0.735501          & 406.819$\pm$127.351 \\
        EI-LP-4 & \textbf{0.284265$\pm$0.24634} &  2.73645$\pm$2.05923                & 18.2682$\pm$0.608564          & 721.351$\pm$327.365 \\
        qKG-4   & 5.59394$\pm$1.80595           &  5.03976$\pm$3.72014                & 18.197$\pm$0.764103           & 705.112$\pm$412.762 \\
        qEI-4   & 2.87373$\pm$1.02405           &  10.1881$\pm$15.0432                & 18.3686$\pm$0.501869          & 655.208$\pm$340.954 \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
acquisition functions. The sequential EI and LCB based Bayesian optimization
are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
respectively.

The mean convergence plots of the tested algorithms on the benchmark functions are
given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE.

@@

\begin{table}[!htb]
    \centering
    \caption{Optimization results of the operational amplifier}
    \label{tab:result_opamp}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & -678.174$\pm$21.7445 \\
        LCB-1     & -607.583$\pm$51.9786 \\
        EI-1      & -532.555$\pm$66.942  \\
        MACE-4    & \textbf{-690.3$\pm$0.104963}  \\
        BLCB-4    & -665.442$\pm$23.066  \\
        EI-LP-4   & -636.675$\pm$35.7359 \\
        \bottomrule
    \end{tabular}
\end{table}

The mean convergence plot for the sequential and batch runs are given in
Figure~\ref{fig:resDAC2014}. The mean and standard deviation of the final
optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
seen, on average, the batch MACE algorithm had the fastest convergence rate
compared with the sequential MACE algorithm and other parallel algorithms. It
should also be noted that the final optimized FOM values given by MACE-4 have
very small deviation (0.105) compared with other algorithms.

@@

\begin{figure}[!htb]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
\end{figure}

@@

@@

\begin{table}[!htb]
    \centering
    \caption{Optimization results of the power amplifier}
    \vskip 0.15in
    \label{tab:result_PA}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results               \\ \midrule
        MACE-1    & -4.08608$\pm$0.296647 \\
        LCB-1     & -3.78533$\pm$0.335532 \\
        EI-1      & -3.36407$\pm$0.307489 \\
        MACE-4    & \textbf{-4.31762$\pm$0.347026} \\
        BLCB-4    & -4.20266$\pm$0.211102 \\
        EI-LP-4   & -4.07233$\pm$0.244436 \\
        \bottomrule
    \end{tabular}
    \vskip -0.1in
\end{table}

For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the Figure of Merit $FOM$ is constructed as
$$
\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}.
$$

@@

\begin{figure}[!htb]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
        \caption{Optimization results of the class-E power amplifier}
        \label{fig:resClassE}
    \end{center}
    \vskip -0.2in
\end{figure}

### 2018-02-09 paper/mace.tex
Paper update

Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}, the multi-objective optimization problem is formulated as
\begin{equation}
    \label{eq:MOFormulation}
    \begin{aligned}
        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x}).
    \end{aligned}
\end{equation}
The multiple objectives to be optimized can be conflicting so that it is usually impossible to find a single solution that is the optimum of all objectives. The goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives. A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$. A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominates at least one point. The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}. It is often unlikely to get the whole Pareto front as there might be infinite points on the Paret front, multi-objective optimization algorithms try to find a set of evenly distributed solutions that approximate the true Pareto front.

@@

\begin{figure*}[htbp]
    \begin{center}
        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
        \caption{Optimization results of the benchmark functions}
        \label{fig:CovPlotBenchmark}
    \end{center}
\end{figure*}

>>>>

Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}. The multi-objective optimization problem is formulated as
\begin{equation}
    \label{eq:MOFormulation}
    \begin{aligned}
        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x}).
    \end{aligned}
\end{equation}
The multiple objectives to be optimized can be conflicting so that it is usually impossible to find a single solution that is the optimum of all objectives. The goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives. A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$. A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominates at least one point. The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}. It is often unlikely to get the whole Pareto front as there might be infinite points on the Paret front, multi-objective optimization algorithms try to find a set of evenly distributed solutions that approximate the true Pareto front.

@@

\begin{figure*}[!htb]
    \begin{center}
        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
        \caption{Optimization results of the benchmark functions}
        \label{fig:CovPlotBenchmark}
    \end{center}
    \vskip -0.15in
\end{figure*}
